DALEX_TechQualityControl

### 2021-02-24 DALEX.Rmd
more plots!

---
title: "DALEX"
author: "Scott Coffin"
date: "2/22/2021"
output: 
  html_document:
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 6
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE, echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
# load required packages
library(rsample)
library(dplyr)
library(DALEX)
library(tidyverse)
library(tigerstats)
library(caret)
library(skimr)
library(ggeffects)
library(knitr)
library(doParallel)
library(modelplotr)
```
# Setup
## Data Import
```{r}
# Load finalized dataset.
aoc <- read_csv("AquaticOrganisms_Clean_final.csv", guess_max = 10000) #%>% 
  #mutate(ID = paste0("ID",row_number()))

@@

# final cleanup and factoring  
aoc_z$Species <- as.factor(paste(aoc_z$genus,aoc_z$species)) #must make value 'Species" (uppercase)
aoc_z$Group <- as.factor(aoc_z$organism.group) #must make value "Group"
aoc_z$Group <- fct_explicit_na(aoc_z$Group) #makes sure that species get counted even if they're missing a group
```
## Data Selection
```{r}
df <- aoc_z %>% 
  dplyr::select(c(organism.group, exposure.duration.d, lvl1_f, dose.um3.mL.master, dose.mg.L.master, dose.particles.mL.master, life.stage, bio.org, polymer, shape, size.length.um.used.for.conversions, treatments, effect, effect.metric, particle.volume.um3, density.mg.um.3, environment, exposure.route, lvl2_f)) %>% 
  mutate(effect.metric = as.character(effect.metric)) %>% 
  mutate(effect.metric = (case_when(
    effect.metric == "NONEC" ~ "NOEC",
    effect.metric == "HONEC" ~ "NOEC",
    effect.metric == "LOEC" ~ "LOEC",
    effect.metric == "LC50" ~ "LC50",
    effect.metric == "EC50" ~"EC50",
    effect.metric == "EC10" ~ "EC10"
  ))) %>% 
  mutate(effect.metric = replace_na(effect.metric,"not_available")) %>% 
  mutate(effect.metric = as.factor(effect.metric)) %>% 
  drop_na() %>%  #drop missing
mutate_if(~is.numeric(.) && (.) > 0, log10) %>% 
  mutate(effect_10 = case_when( #convert ordinal to numeric
      effect == "Y" ~ 1,
      effect == "N" ~ 0
    )) %>%
  mutate(effect_10 = factor(effect_10)) %>% 
  dplyr::select(-(effect))

@@

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Examine the environment to be sure # of observations looks like the 75/25 split. 3199:1066.
classif_rf <- train(effect_10~., data = train, method = "rf", ntree = 100, tuneLength = 1)

@@

```
# Modelling
## Model Performance
```{r}
mp_classif_rf <- model_performance(explainer_classif_rf)
mp_classif_glm <- model_performance(explainer_classif_glm)
mp_classif_svm <- model_performance(explainer_classif_svm)
mp_classif_decTree <- model_performance(explainer_classif_decTree)
mp_classif_nnet <- model_performance(explainer_classif_nnet)
mp_classif_xgbTree <- model_performance(explainer_classif_xgbTree)
#mp_classif_logicBag <- model_performance(explainer_classif_logicBag)

# compare residuals plots
resid_dist <- plot(mp_classif_rf, mp_classif_glm, mp_classif_svm, mp_classif_decTree, mp_classif_nnet,
                   mp_classif_xgbTree) + #, mp_classif_logicBag) +
  theme_minimal() +
        theme(legend.position = 'bottom',
              plot.title = element_text(hjust = 0.5)) + 
        labs(y = '')
resid_dist
```
#### Residuals
```{r}
resid_box <- plot(mp_classif_rf, mp_classif_glm, mp_classif_svm, mp_classif_decTree, mp_classif_nnet, mp_classif_xgbTree,
     #mp_classif_logicBag, 
     geom = "boxplot") +
  theme_minimal() +
        theme(legend.position = 'bottom',
              plot.title = element_text(hjust = 0.5)) 
resid_box
```
```{r}
require(gridExtra)
grid.arrange(resid_box,resid_dist, ncol=2)
```

#### Lift Curves

@@

#### Roc Curves
```{r}
plot(mp_classif_rf, 
     #mp_classif_glm, 
     mp_classif_svm, 
     #mp_classif_decTree, 
     mp_classif_nnet,
     #mp_classif_xgbTree,
     geom = "roc") +
  ggtitle("ROC Curves - All Models",  
          paste("AUC_rf = ",round(mp_classif_rf$measures$auc,2), 
                paste("AUC_svm = ",round(mp_classif_svm$measures$auc,2)),
          paste("AUC_nnet = ",round(mp_classif_nnet$measures$auc,2))
          )) +
#,  "AUC_glm = 0.799  AUC_svm = 0.798 AUC_decTree = AUC_nnet = AUC_xgbTree = ") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

@@

#### Partial Dependence Plot
```{r}
pdp_classif_rf  <- model_profile(explainer_classif_rf, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_glm  <- model_profile(explainer_classif_glm, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_svm  <- model_profile(explainer_classif_svm, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_decTree  <- model_profile(explainer_classif_decTree, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_nnet  <- model_profile(explainer_classif_nnet, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_xgbTree  <- model_profile(explainer_classif_xgbTree, variable = "dose.um3.mL.master", type = "partial")
#pdp_classif_logicBag  <- model_profile(explainer_classif_logicBag, variable = "dose.um3.mL.master", type = "partial")

plot(pdp_classif_rf, pdp_classif_glm, pdp_classif_svm, pdp_classif_decTree, pdp_classif_nnet, pdp_classif_xgbTree)#, pdp_classif_logicBag)
```
```{r}
#Partial Dependence organism type
pdp_classif_rf  <- model_profile(explainer_classif_rf, variable = "organism.group", type = "partial")
pdp_classif_glm  <- model_profile(explainer_classif_glm, variable = "organism.group", type = "partial")
pdp_classif_svm  <- model_profile(explainer_classif_svm, variable = "organism.group", type = "partial")
pdp_classif_decTree  <- model_profile(explainer_classif_decTree, variable = "organism.group", type = "partial")
pdp_classif_nnet  <- model_profile(explainer_classif_nnet, variable = "organism.group", type = "partial")
pdp_classif_xgbTree  <- model_profile(explainer_classif_xgbTree, variable = "organism.group", type = "partial")
#pdp_classif_logicBag  <- model_profile(explainer_classif_logicBag, variable = "dose.um3.mL.master", type = "partial")

@@

#### Breakdown

@@

## Tuning
http://rstudio-pubs-static.s3.amazonaws.com/480890_237ad52b09b6440e9c849a3c07a04d2f.html
```{r include=FALSE}
cache = TRUE
set.seed(1000)
train_control <- trainControl(method = "repeatedcv", 
                              number = 10,
                              repeats = 5,
                              verboseIter = TRUE,
                              allowParallel = TRUE,
                              summaryFunction = multiClassSummary)
cache = TRUE
set.seed(1000)

@@

```{r}

@@

### Final Model
Now that we have optimized the variables for our final model, we will build and save the final simplified model that has the highest accuracy.
```{r}
tunegrid <- expand.grid(.mtry=c(7))

>>>>

---
title: "DALEX_TechQualityControl"
author: "Scott Coffin"
date: "2/23/2021"
output: 
  html_document:
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 6
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE, echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
# load required packages
library(rsample)
library(dplyr)
library(DALEX)
library(tidyverse)
library(tigerstats)
library(caret)
library(skimr)
library(ggeffects)
library(knitr)
library(doParallel)
library(modelplotr)
library(gridExtra)
```
# Setup
## Data Import
```{r}
# Load finalized dataset.
aoc <- read_csv("AquaticOrganisms_Clean_final.csv", guess_max = 10000) #%>% 
  #mutate(ID = paste0("ID",row_number()))

@@

# final cleanup and factoring  
aoc_z$Species <- as.factor(paste(aoc_z$genus,aoc_z$species)) #must make value 'Species" (uppercase)
aoc_z$Group <- as.factor(aoc_z$organism.group) #must make value "Group"
aoc_z$Group <- fct_explicit_na(aoc_z$Group) #makes sure that species get counted even if they're missing a group
```
## Data Selection
```{r}
df <- aoc_z %>% 
  filter(tech.tier.zero == "N") %>% #gives studies that pass technical quality criteria
  dplyr::select(c(organism.group, exposure.duration.d, lvl1_f, dose.um3.mL.master, dose.mg.L.master, dose.particles.mL.master, life.stage, bio.org, polymer, shape, size.length.um.used.for.conversions, treatments, effect, effect.metric, particle.volume.um3, density.mg.um.3, environment, exposure.route, lvl2_f)) %>% 
  mutate(effect.metric = as.character(effect.metric)) %>% 
  mutate(effect.metric = (case_when(
    effect.metric == "NONEC" ~ "NOEC",
    effect.metric == "HONEC" ~ "NOEC",
    effect.metric == "LOEC" ~ "LOEC",
    effect.metric == "LC50" ~ "LC50",
    effect.metric == "EC50" ~"EC50",
    effect.metric == "EC10" ~ "EC10"
  ))) %>% 
  mutate(effect.metric = replace_na(effect.metric,"not_available")) %>% 
  mutate(effect.metric = as.factor(effect.metric)) %>% 
  drop_na() %>%  #drop missing
mutate_if(~is.numeric(.) && (.) > 0, log10) %>% 
  mutate(effect_10 = case_when( #convert ordinal to numeric
      effect == "Y" ~ 1,
      effect == "N" ~ 0
    )) %>%
  mutate(effect_10 = factor(effect_10)) %>% 
  dplyr::select(-(effect))

@@

```{r All Model Training, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Examine the environment to be sure # of observations looks like the 75/25 split. 3199:1066.
classif_rf <- train(effect_10~., data = train, method = "rf", ntree = 100, tuneLength = 1)

@@

```
# Modelling
## Model Performance
```{r model performance, include=FALSE}
mp_classif_rf <- model_performance(explainer_classif_rf)
mp_classif_glm <- model_performance(explainer_classif_glm)
mp_classif_svm <- model_performance(explainer_classif_svm)
mp_classif_decTree <- model_performance(explainer_classif_decTree)
mp_classif_nnet <- model_performance(explainer_classif_nnet)
mp_classif_xgbTree <- model_performance(explainer_classif_xgbTree)
#mp_classif_logicBag <- model_performance(explainer_classif_logicBag)
```

### Histogram of Residuals
```{r}
plot(mp_classif_rf, mp_classif_glm, geom ="histogram")
```
```{r}
plot(mp_classif_svm, mp_classif_decTree, geom ="histogram")
```

```{r}
plot(mp_classif_nnet, mp_classif_xgbTree, geom ="histogram")
```
### Precision Recall Curves
```{r}
plot(mp_classif_rf, mp_classif_glm, mp_classif_svm, mp_classif_decTree, mp_classif_nnet, mp_classif_xgbTree, geom ="prc")
```

### Reverse Cumulative Distribution of Residuals
```{r}
# compare residuals plots
resid_dist <- plot(mp_classif_rf, mp_classif_glm, mp_classif_svm, mp_classif_decTree, mp_classif_nnet,
                   mp_classif_xgbTree) + #, mp_classif_logicBag) +
  theme_minimal() +
        theme(legend.position = 'bottom',
              plot.title = element_text(hjust = 0.5)) + 
        labs(y = '')
resid_dist
```
#### Residuals
```{r}
resid_box <- plot(mp_classif_rf, mp_classif_glm, mp_classif_svm, mp_classif_decTree, mp_classif_nnet, mp_classif_xgbTree,
     #mp_classif_logicBag, 
     geom = "boxplot") +
  theme_minimal() +
        theme(legend.position = 'bottom',
              plot.title = element_text(hjust = 0.5)) 
resid_box
```
```{r}
require(gridExtra)
grid.arrange(resid_box,resid_dist, ncol=2)
```

### Lift Curves

@@

### Roc Curves
```{r}
plot(mp_classif_rf, 
     #mp_classif_glm, 
     mp_classif_svm, 
     #mp_classif_decTree, 
     mp_classif_nnet,
     #mp_classif_xgbTree,
     geom = "roc") +
  ggtitle("ROC Curves - All Models",  
          paste("AUC_rf = ",round(mp_classif_rf$measures$auc,3), 
                paste("AUC_svm = ",round(mp_classif_svm$measures$auc,3)),
          paste("AUC_nnet = ",round(mp_classif_nnet$measures$auc,3))
          )) +
#,  "AUC_glm = 0.799  AUC_svm = 0.798 AUC_decTree = AUC_nnet = AUC_xgbTree = ") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

@@

### Partial Dependence Plot
```{r}
pdp_classif_rf  <- model_profile(explainer_classif_rf, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_glm  <- model_profile(explainer_classif_glm, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_svm  <- model_profile(explainer_classif_svm, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_decTree  <- model_profile(explainer_classif_decTree, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_nnet  <- model_profile(explainer_classif_nnet, variable = "dose.um3.mL.master", type = "partial")
pdp_classif_xgbTree  <- model_profile(explainer_classif_xgbTree, variable = "dose.um3.mL.master", type = "partial")
#pdp_classif_logicBag  <- model_profile(explainer_classif_logicBag, variable = "dose.um3.mL.master", type = "partial")

plot(pdp_classif_rf, pdp_classif_glm, pdp_classif_svm, pdp_classif_decTree, pdp_classif_nnet, pdp_classif_xgbTree)#, pdp_classif_logicBag)
```

```{r}
#Partial Dependence organism type
pdp_classif_rf  <- model_profile(explainer_classif_rf, variable = "organism.group", type = "partial")
pdp_classif_glm  <- model_profile(explainer_classif_glm, variable = "organism.group", type = "partial")
pdp_classif_svm  <- model_profile(explainer_classif_svm, variable = "organism.group", type = "partial")
pdp_classif_decTree  <- model_profile(explainer_classif_decTree, variable = "organism.group", type = "partial")
pdp_classif_nnet  <- model_profile(explainer_classif_nnet, variable = "organism.group", type = "partial")
pdp_classif_xgbTree  <- model_profile(explainer_classif_xgbTree, variable = "organism.group", type = "partial")
#pdp_classif_logicBag  <- model_profile(explainer_classif_logicBag, variable = "dose.um3.mL.master", type = "partial")

@@

##### Grouped Partial Dependence Plots
```{r include=FALSE}
plot(pdp_classif_rf)
#Partial Dependence by dose.particles.mL.master and effect.metric
pdp_classif_rf  <- model_profile(explainer_classif_rf, variable = "dose.particles.mL.master", 
                                 groups = "effect.metric")
pdp_classif_glm  <- model_profile(explainer_classif_glm, variable = "dose.particles.mL.master", 
                                 groups = "effect.metric")
pdp_classif_svm  <- model_profile(explainer_classif_svm, variable = "dose.particles.mL.master", 
                                 groups = "effect.metric")
pdp_classif_decTree  <- model_profile(explainer_classif_decTree, variable = "dose.particles.mL.master", 
                                 groups = "effect.metric")
pdp_classif_nnet  <- model_profile(explainer_classif_nnet, variable = "dose.particles.mL.master", 
                                 groups = "effect.metric")
pdp_classif_xgbTree  <- model_profile(explainer_classif_xgbTree, variable = "dose.particles.mL.master", 
                                 groups = "effect.metric")
```

```{r}
#plot neural net and glm
glm <- plot(pdp_classif_glm$agr_profiles) +
  ggtitle("GLM: Partial Dependence Profiles by Dose and Effect Metric", "") +
  xlab("log10(dose particles/mL)") +
  ylab("Average Prediction for Effect (1 = yes, 0 = no)") +
  scale_color_discrete(name = "Model x Effect Metric") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

nnet <- plot(pdp_classif_nnet$agr_profiles) +
  ggtitle("Neural Net: Partial Dependence Profiles by Dose and Effect Metric", "") +
  xlab("log10(dose particles/mL)") +
  ylab("Average Prediction for Effect (1 = yes, 0 = no)") +
  scale_color_discrete(name = "Model x Effect Metric") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
grid.arrange(glm, nnet)
```

```{r}
#plot rf and decision tree
rf <- plot(pdp_classif_rf$agr_profiles) +
  ggtitle("Random Forest:Partial Dependence Profiles by Dose and Effect Metric", "") +
  xlab("log10(dose particles/mL)") +
  ylab("Average Prediction for Effect (1 = yes, 0 = no)") +
  scale_color_discrete(name = "Model x Effect Metric") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

decTree <- plot(pdp_classif_decTree$agr_profiles) +
  ggtitle("Decision Tree: Partial Dependence Profiles by Dose and Effect Metric", "") +
  xlab("log10(dose particles/mL)") +
  ylab("Average Prediction for Effect (1 = yes, 0 = no)") +
  scale_color_discrete(name = "Model x Effect Metric") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
grid.arrange(rf, decTree)
```

```{r}
#plot rf and decision tree
svm <- plot(pdp_classif_svm$agr_profiles) +
  ggtitle("Support Vector Machine:Partial Dependence Profiles by Dose and Effect Metric", "") +
  xlab("log10(dose particles/mL)") +
  ylab("Average Prediction for Effect (1 = yes, 0 = no)") +
  scale_color_discrete(name = "Model x Effect Metric") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

xgbTree <- plot(pdp_classif_xgbTree$agr_profiles) +
  ggtitle("eXtreme Gradient Boosing Trees: Partial Dependence Profiles by Dose and Effect Metric", "") +
  xlab("log10(dose particles/mL)") +
  ylab("Average Prediction for Effect (1 = yes, 0 = no)") +
  scale_color_discrete(name = "Model x Effect Metric") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
grid.arrange(svm, xgbTree)
```

### Confusion Matrices

```{r include=FALSE}
#predict test data
pred_rf <- predict(classif_rf, newdata = test)
pred_glm <- predict(classif_glm, newdata = test)
pred_svm <- predict(classif_svm, newdata = test)
pred_decTree <- predict(classif_decTree, newdata = test)
pred_nnet <- predict(classif_nnet, newdata = test)
pred_xgbTree <- predict(classif_xgbTree, newdata = test)

#build confusion matrices
table_rf <- data.frame(confusionMatrix(pred_rf, test$effect_10)$table)
table_glm <- data.frame(confusionMatrix(pred_glm, test$effect_10)$table)
table_svm <- data.frame(confusionMatrix(pred_svm, test$effect_10)$table)
table_decTree <- data.frame(confusionMatrix(pred_decTree, test$effect_10)$table)
table_nnet <- data.frame(confusionMatrix(pred_nnet, test$effect_10)$table)
table_xgbTree <- data.frame(confusionMatrix(pred_xgbTree, test$effect_10)$table)

#build plots
plotTable_rf <- table_rf %>% mutate(goodbad = ifelse(table_rf$Prediction == table_rf$Reference, "good", "bad")) %>%
  group_by(Reference) %>% mutate(prop = Freq/sum(Freq))

plotTable_glm <- table_glm %>% mutate(goodbad = ifelse(table_glm$Prediction == table_glm$Reference, "good", "bad")) %>%
  group_by(Reference) %>% mutate(prop = Freq/sum(Freq))

plotTable_svm <- table_svm %>% mutate(goodbad = ifelse(table_svm$Prediction == table_svm$Reference, "good", "bad")) %>%
  group_by(Reference) %>% mutate(prop = Freq/sum(Freq))

plotTable_decTree <- table_decTree %>% mutate(goodbad = ifelse(table_decTree$Prediction == table_decTree$Reference, "good", "bad")) %>%
  group_by(Reference) %>% mutate(prop = Freq/sum(Freq))

plotTable_nnet <- table_nnet %>% mutate(goodbad = ifelse(table_nnet$Prediction == table_nnet$Reference, "good", "bad")) %>%
  group_by(Reference) %>% mutate(prop = Freq/sum(Freq))

plotTable_xgbTree <- table_xgbTree %>% mutate(goodbad = ifelse(table_xgbTree$Prediction == table_xgbTree$Reference, "good", "bad")) %>%
  group_by(Reference) %>% mutate(prop = Freq/sum(Freq))
```

Confusion Matrices for the six tested models are below.
```{r}
# fill alpha relative to sensitivity/specificity by proportional outcomes within reference groups (see dplyr code above as well as original confusion matrix for comparison)
CM_rf <- ggplot(data = plotTable_rf, mapping = aes(x = Reference, y = Prediction, fill = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_gradient(low = "white", high = "cyan4", name = "Proportion") +
  scale_x_discrete(labels = c("No Effect", "Effect")) +
  scale_y_discrete(labels = c("No Effect", "Effect")) +
  ggtitle("Random Forest",
          paste("Accuracy = ", 100 * round(mp_classif_rf$measures$accuracy,3), "%")) +
  theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
          legend.position = "none")

CM_glm <- ggplot(data = plotTable_glm, mapping = aes(x = Reference, y = Prediction, fill = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_gradient(low = "white", high = "cyan4", name = "Proportion") +
  scale_x_discrete(labels = c("No Effect", "Effect")) +
  scale_y_discrete(labels = c("No Effect", "Effect")) +
  ggtitle("General Linear Model",
          paste("Accuracy = ", 100 * round(mp_classif_glm$measures$accuracy,3), "%")) +
  theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
          legend.position = "none")

CM_svm <- ggplot(data = plotTable_svm, mapping = aes(x = Reference, y = Prediction, fill = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_gradient(low = "white", high = "cyan4", name = "Proportion") +
  scale_x_discrete(labels = c("No Effect", "Effect")) +
  scale_y_discrete(labels = c("No Effect", "Effect")) +
  ggtitle("Support Vector Machine",
          paste("Accuracy = ", 100 * round(mp_classif_svm$measures$accuracy,3), "%")) +
  theme_bw() +
 theme(plot.title = element_text(hjust = 0.5),
          legend.position = "none")

CM_decTree <- ggplot(data = plotTable_decTree, mapping = aes(x = Reference, y = Prediction, fill = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_gradient(low = "white", high = "cyan4", name = "Proportion") +
  scale_x_discrete(labels = c("No Effect", "Effect")) +
  scale_y_discrete(labels = c("No Effect", "Effect")) +
  ggtitle("Decision Tree",
          paste("Accuracy = ", 100 * round(mp_classif_decTree$measures$accuracy,3), "%")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
          legend.position = "none")

CM_nnet <- ggplot(data = plotTable_nnet, mapping = aes(x = Reference, y = Prediction, fill = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_gradient(low = "white", high = "cyan4", name = "Proportion") +
  scale_x_discrete(labels = c("No Effect", "Effect")) +
  scale_y_discrete(labels = c("No Effect", "Effect")) +
  ggtitle("Neural Net",
          paste("Accuracy = ", 100 * round(mp_classif_nnet$measures$accuracy,3), "%")) +
  theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
          legend.position = "none")

CM_xgbTree <- ggplot(data = plotTable_xgbTree, mapping = aes(x = Reference, y = Prediction, fill = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_gradient(low = "white", high = "cyan4", name = "Proportion") +
  scale_x_discrete(labels = c("No Effect", "Effect")) +
  scale_y_discrete(labels = c("No Effect", "Effect")) +
  ggtitle("eXtreme Gradient Boosting Trees",
          paste("Accuracy = ", 100 * round(mp_classif_xgbTree$measures$accuracy,3), "%")) +
  theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
          legend.position = "none")

grid.arrange(CM_rf, CM_glm, CM_svm, CM_decTree, CM_nnet, CM_xgbTree,
             ncol = 2, top = "Confusion Matrices for ML Models")
```

### Breakdown

@@

## Tuning
http://rstudio-pubs-static.s3.amazonaws.com/480890_237ad52b09b6440e9c849a3c07a04d2f.html
```{r Tuning, include=FALSE}
cache = TRUE
set.seed(1000)
train_control <- trainControl(method = "repeatedcv", 
                              number = 10,
                              repeats = 5,
                              verboseIter = TRUE,
                              allowParallel = TRUE,
                              summaryFunction = multiClassSummary)
cache = TRUE
set.seed(1000)

@@

```{r Recursive Feature Elimination}

@@

### Final Model
Now that we have optimized the variables for our final model, we will build and save the final simplified model that has the highest accuracy.
```{r Final Model}
tunegrid <- expand.grid(.mtry=c(7))
